Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

The model is made up of two different materials, together with several already mentioned ideally rigid parts (see \cref{sec:impact}). The adherends of the tube are made of elastic-plastic steel. The adhesive is an elastic material only considering one normal and two shear directions with a damage formulation.

Loctite Hysol 9514 \cite{manufCatalog} was the chosen adhesive for the bonding, for its shown interest by many other authors for structural bonding \cite{Sadowski2010, Scattina2011, SernaMoreno2015}, making it an \textit{a priori} good candidate for the studied application. It is a monocomponent epoxy adhesive which requires heat curing processes in the union cast.

According to \cite{manufCatalog}, the shear strength of the adhesive is $\SI{44}{\MPa}$, although this parameter is subject to variation depending both in cure temperature and time. Dependency can be seen on \cref{fig:catalog_temp}. Given value corresponds to a $\SI{150}{\celsius}$ cure for $\SI{30}{\min}$. The bulk modulus is $\SI{1460}{\MPa}$ and the adhesive's density is $\SI{1.46}{\tonne/\m^3}$ \cite{manufCatalog}.

>>>>

The model is made up of two different materials: the adherends of the tube are made of steel and the adhesive is the epoxy-based, heat-cured Loctite Hysol 9514.

According to \cite{manufCatalog}, the shear strength of the adhesive is $\SI{44}{\MPa}$, although this parameter is subject to variation depending both in cure temperature and time. The bulk modulus is $\SI{1460}{\MPa}$ and the adhesive's density is $\SI{1.30}{\tonne/\m^3}$ \cite{manufCatalog}.
